`r params$doc_title`

### 2023-05-09 scripts/MSc.Rmd
highlighted best methods in barplots 2

p1.gsd+
  ggthemes::theme_few() -> p1.gsd

@@

    df.temp.long[[ref.method]] %>%
      mutate(N=paste0("Sample Size: ", format(N, scientific=FALSE))) %>% 
      mutate(label.too.large = ifelse(mse>my.y.lim, paste0("MSE \u2265 ", my.y.lim) , NA)) %>%
      filter(Scenario == scenarios[scenario]) %>% 
      ## DROP NA (e.g. no sample sizes 50.000)
      drop_na(Mean) %>%  
      group_by(N) %>% 
      mutate(smallest_mse = mse == min(mse)) %>% # add a new column to identify the rows with the smallest mse value within each group
      ungroup() %>% 
      # PLOT
      ggplot(aes(x=Method, y=mse)) +
      geom_bar(
        aes(fill = smallest_mse), # add fill aesthetics to highlight the bars with the smallest mse value within each group
        stat="identity", position=position_dodge2(reverse=TRUE),
        #color=ggthemes_data$few$colors$Dark[2,2][[1]],
      ) +   # reverse dodge
      geom_text(aes(x= Method, y= my.y.lim, label = label.too.large,
                    colour=label.too.large), #position = position_dodge(),
                nudge_y = -0.1, #size = 2.25, angle = 90
                color=ggthemes_data$few$colors$Dark[4,2][[1]],
                fontface="bold"
      )+
      facet_wrap(~N, nrow = 4) + 
      xlab("Method")+
      ylab(paste0("Mean Squared Error with nsim=", nsim))+
      labs(#title = paste0("Selected Reference Method: ", 
          #                selected_true_methods[ref.method]),
           #subtitle = paste0("Genetic Architecture: ", scenarios[scenario])
      )+
      #ylim(0, 0.5)+
      coord_flip(ylim=c(0, my.y.lim))+
      ggthemes::theme_few()+  # remove legend
      scale_fill_manual(values = c("gray80", "blue"), guide = "none") -> dodged.barplot.mse.scenario[[scenario]]

@@

  # scenarios WITHOUT all instruments in arranged plot
  arrangedplot.mse.scenarios <- 
    ggarrange(plotlist = dodged.barplot.mse.scenario[-1], labels = c("A", "B", "C", "D", "E", "F"))
  plot(arrangedplot.mse.scenarios)
  if (SAVE.files ==TRUE ){
        ## arranged plots are toooo small 
        filename.arrangedplot.mse.scenarios <- paste0("./output/plots/summary-plots/arranged_scenarios/",
                                              Sys.Date(), "_mse_GSD_dodged_barplot_REF_METHOD_",
                                              selected_true_methods[ref.method], "_NSIM_", nsim)
        ggsave(filename = paste0(filename.arrangedplot.mse.scenarios, ".svg"), 
               plot = arrangedplot.mse.scenarios, 
               width = 10, height = 12, 
               units = "in"  # default
               )
  }

@@

    df.temp.long[[ref.method]] %>%
      mutate(N=paste0("Sample Size: ", format(N, scientific=FALSE))) %>% 
      filter(Scenario == scenarios[scenario]) %>% 
      ## DROP NA (e.g. no sample sizes 50.000)
      drop_na(Mean) %>%  
      ggplot(aes(x=Method, y=bias)) +
      geom_bar(stat="identity", position=position_dodge2(reverse=TRUE),
               #color=ggthemes_data$few$colors$Dark[2,2][[1]],
               ) +   # reverse dodge
      geom_hline(yintercept = 0,  col=ggthemes_data$few$colors$Dark[3,2][[1]], alpha=0.6)+
      facet_wrap(~N, nrow = 4) + 
      xlab("Method")+
      ylab(paste0("Bias with nsim=", nsim))+
      labs(title = paste0("Selected Reference Method: ", 
                              selected_true_methods[ref.method]),
           subtitle = paste0("Genetic Architecture: ", scenarios[scenario])
           )+
      #ylim(0, 0.5)+
      coord_flip()+
      ggthemes::theme_few()+  # remove legend
      ggthemes::scale_fill_few() -> dodged.barplot.bias.scenario[[scenario]]

@@

   # scenarios without all instruments in arranged plot
  arrangedplot.bias.scenarios <- 
    ggarrange(plotlist = dodged.barplot.bias.scenario[-1], labels = c("A", "B", "C", "D", "E", "F"))

@@

arrangedplot.bias.references <- 
    ggarrange(plotlist = dodged.barplot.bias.references.update, labels = c("A", "B", "C", "D", "E", "F"), ncol=3, nrow=2)

@@

>>>>

p1.gsd+
  xlab("SNP effect on BMI")+
  ylab("SNP effect on GSD")+
  ggthemes::theme_few() -> p1.gsd

@@

    df.temp.long[[ref.method]] %>%
      mutate(N=paste0("Sample Size: ", format(N, scientific=FALSE))) %>% 
      mutate(label.too.large = ifelse(mse>my.y.lim, paste0("MSE \u2265 ", my.y.lim) , NA)) %>%
      filter(Scenario == scenarios[scenario]) %>% 
      ## DROP NA (e.g. no sample sizes 50.000)
      drop_na(Mean) %>%  
      group_by(N) %>% 
      mutate(smallest_mse = mse == min(mse)) %>% # add a new column to identify the rows with the smallest mse value within each group
      ungroup() %>% 
      # PLOT
      ggplot(aes(x=Method, y=mse)) +
      geom_bar(
        aes(fill = smallest_mse), # add fill aesthetics to highlight the bars with the smallest mse value within each group
        stat="identity", position=position_dodge2(reverse=TRUE),
        #color=ggthemes_data$few$colors$Dark[2,2][[1]],
      ) +   # reverse dodge
      geom_text(aes(x= Method, y= my.y.lim, label = label.too.large,
                    colour=label.too.large), #position = position_dodge(),
                nudge_y = -0.1, #size = 2.25, angle = 90
                color=ggthemes_data$few$colors$Dark[4,2][[1]],
                fontface="bold"
      )+
      facet_wrap(~N, nrow = 4) + 
      xlab("Method")+
      ylab(paste0("Mean Squared Error with nsim=", nsim))+
      labs(#title = paste0("Selected Reference Method: ", 
          #                selected_true_methods[ref.method]),
           #subtitle = paste0("Genetic Architecture: ", scenarios[scenario])
      )+
      #ylim(0, 0.5)+
      coord_flip(ylim=c(0, my.y.lim))+
      ggthemes::theme_few()+  # remove legend
      scale_fill_manual(values = c("gray80", color.bar), guide = "none") -> dodged.barplot.mse.scenario[[scenario]]

@@

  # scenarios WITHOUT all instruments in arranged plot

  # make smaller plots
  base_theme <- theme_few(base_size = 8)
  for (smallplot in seq_along(dodged.barplot.mse.scenario)) {
    dodged.barplot.mse.scenario[[smallplot]] <- dodged.barplot.mse.scenario[[smallplot]] +
      base_theme
  }

  arrangedplot.mse.scenarios <- 
    ggarrange(plotlist = dodged.barplot.mse.scenario[-1], labels = c("Scenario 2", "Scenario 3", "Scenario 4", "Scenario 5"))
  plot(arrangedplot.mse.scenarios)
  if (SAVE.files ==TRUE ){
        ## arranged plots are toooo small 
        filename.arrangedplot.mse.scenarios <- paste0("./output/plots/summary-plots/arranged_scenarios/",
                                              Sys.Date(), "_mse_GSD_dodged_barplot_REF_METHOD_",
                                              selected_true_methods[ref.method], "_NSIM_", nsim)
        ggsave(filename = paste0(filename.arrangedplot.mse.scenarios, ".svg"), 
               plot = arrangedplot.mse.scenarios, 
               width = 10, height = 12, 
               units = "in"  # default
               )
  }

@@

    df.temp.long[[ref.method]] %>%
      mutate(N=paste0("Sample Size: ", format(N, scientific=FALSE))) %>% 
      filter(Scenario == scenarios[scenario]) %>% 
      ## DROP NA (e.g. no sample sizes 50.000)
      drop_na(Mean) %>%  
      group_by(N) %>% 
      mutate(smallest_bias = abs(bias) == min(abs(bias))) %>% # add a new column to identify the rows with the smallest bias value
      ungroup() %>% 
      # PLOT
      ggplot(aes(x=Method, y=bias)) +
      geom_bar(
        aes(fill = smallest_bias), # add fill aesthetics to highlight the bars with the smallest mse value within each group
        stat="identity", position=position_dodge2(reverse=TRUE),
        #color=ggthemes_data$few$colors$Dark[2,2][[1]],
      ) +   # reverse dodge
      geom_hline(yintercept = 0,  col=ggthemes_data$few$colors$Dark[3,2][[1]], alpha=0.6)+
      facet_wrap(~N, nrow = 4) + 
      xlab("Method")+
      ylab(paste0("Bias with nsim=", nsim))+
      labs(#title = paste0("Selected Reference Method: ", 
           #               selected_true_methods[ref.method]),
           #subtitle = paste0("Genetic Architecture: ", scenarios[scenario])
      )+
      #ylim(0, 0.5)+
      coord_flip()+
      ggthemes::theme_few()+  # remove legend
      scale_fill_manual(values = c("gray80", color.bar), guide = "none") -> dodged.barplot.bias.scenario[[scenario]]

@@

  # make smaller plots
  base_theme <- theme_few(base_size = 8)
  for (smallplot in seq_along(dodged.barplot.bias.scenario)) {
    dodged.barplot.bias.scenario[[smallplot]] <- dodged.barplot.bias.scenario[[smallplot]] +
      base_theme
  }

  arrangedplot.bias.scenarios <- 
    ggarrange(plotlist = dodged.barplot.bias.scenario[-1], labels = c("Scenario 2", "Scenario 3", "Scenario 4", "Scenario 5"))

@@

## all methods compared 
arrangedplot.bias.references <- 
    ggarrange(plotlist = dodged.barplot.bias.references.update, labels = c("A", "B", "C", "D", "E", "F"), ncol=3, nrow=2)

@@

# Figure 10/11 MSE and BIAS in Scenario 1 with ref estimate FTO Wald
names(dodged.barplot.mse.references) <- names(df_metrics_all_scenarios)
names(dodged.barplot.bias.references) <- names(df_metrics_all_scenarios)
arranged.msebias.scenario1.fto <- ggarrange(dodged.barplot.mse.references$ref_FTO_Wald, dodged.barplot.bias.references$ref_FTO_Wald, ncol=2, labels = c("A", "B"))
arranged.msebias.scenario1.mrmix <- ggarrange(dodged.barplot.mse.references$ref_MRMix, dodged.barplot.bias.references$ref_MRMix, ncol=2, labels = c("A", "B"))

if (SAVE.files ==TRUE ){
    ## arranged plots are toooo small 
    filename.arranged.msebias.scenario1.fto <- paste0("./output/plots/summary-plots/figure10/", Sys.Date(), "_bias_mse_barplot_REF_METHOD_FTO_WALD_NSIM_", nsim)
    filename.arranged.msebias.scenario1.mrmix <- paste0("./output/plots/summary-plots/figure10/", Sys.Date(), "_bias_mse_barplot_REF_METHOD_MRMIX_NSIM_", nsim)

    ggsave(filename = paste0(filename.arranged.msebias.scenario1.fto, ".svg"), plot =  arranged.msebias.scenario1.fto, 
             width = 8, height = 7, 
             units = "in"  # default
             )
    ggsave(filename = paste0(filename.arranged.msebias.scenario1.mrmix, ".svg"), plot =  arranged.msebias.scenario1.mrmix, 
             width = 8, height = 7, 
             units = "in"  # default
             )
}
